Simulated Probabilistic Distributions

### 2021-07-28 App_Nonessential/simulated-distributions_crustDev.Rmd
Moved all scripts that are non essential to the app to a seperate folder since they are interferring with deployment

```{r}
#prediction paramaters
Data <- Data %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Mortality")
```

@@

#### Determine which variables are most available
```{r}
#determine which lvl2_f are most abundant for crustacea data
crust <- aoc_z %>% 
  dplyr::select(c(life.stage, bio.org, effect.metric, environment, exposure.route, lvl2_f, exposure.duration.d, treatments, lvl1_f, organism.group, dose.particles.mL.master, dose.mg.L.master, effect_f, effect_10, size.length.um.used.for.conversions, density.mg.um.3, csf)) %>% 
 #filter(treatments == 4) %>% 
  filter(organism.group == "Crustacea") %>% 
  filter(exposure.duration.d == 14) %>% 
  filter(lvl1_f == "Fitness") %>% 
  #filter(life.stage == "Early") %>% 
  filter(bio.org == "organism") %>% 
 # filter(effect.metric == "NOEC") %>% 
  #filter(environment == "Marine") %>% 
  filter(exposure.route == "water") %>% 
 filter(lvl2_f == "Mortality")

@@

df_pred %>% ggplot(aes(x = factor(vol.L), y = ToxicityProbability)) + 
  stat_ecdf(geom = "point", size = 2, color = "blue")+
  stat_ecdf(geom = "step", linetype = 'solid', alpha = 0.6, size = 1.5) +
  #scale_x_log10() +
  scale_y_continuous(labels = scales::percent)+
  labs(title = "Cumulative Toxicity Probability",
       subtitle = "n = 1000 particles/L; Crustacea acute Mortality",
       caption = "Predicted Toxicity from Random Forest")
```

@@

Data_5p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Mortality") %>% 
  mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("5p"))
```

@@

Data_10p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Mortality") %>% 
  mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("10p"))
```
### 20 particles in 1 L
```{r, include=FALSE}
#rm(list=ls())
n = 20
## Generate values for the three distributions
set.seed(123)

@@

Data_20p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Mortality") %>% 
  mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("20p"))
```

@@

Data_40p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Mortality") %>% 
  mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>%  
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("40p"))
```

@@

Data_80p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Mortality") %>% 
  mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("80p"))
```

@@

Data_160p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Mortality") %>% 
  mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("160p"))
```

@@

Data_320p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Mortality") %>% 
 mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("320p"))
```

@@

Data_480p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Mortality") %>% 
 mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("480p"))
```

@@

Data_640p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Mortality") %>% 
 mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>%  
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("640p"))
```

@@

Data_1000p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Mortality") %>% 
 mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("1000p"))
```

@@

Data_1280p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Mortality") %>% 
 mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("1280p"))
```

@@

#plot dose response relationship
prob_summ %>% 
  ggplot(aes(x = particles, y = probability)) +
  geom_point() + 
  stat_smooth(method = drm, method.args = list(fct = LL.4()), se = FALSE) + #logit-4 paramater curve
  scale_x_log10(name = "Particles/mL (1-5,000 um)") +
  scale_y_continuous(labels = scales::percent_format(),
                     name = "Probability of NOEC") +
  labs(title = "Model-Predicted Probability of Toxicity",
       subtitle = "Crustacea; 14-d exp; Mortality; NOEC; Early; Marine",
       caption = "Random Forest Model; Simulated particle distribution (alpha = 1.6)") +
  theme_minimal(base_size = 14) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

>>>>

```{r}
#prediction paramaters
Data <- Data %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Development")
```

@@

#### Determine which variables are most available
```{r}
#determine which lvl2_f are most abundant for crustacea data
crust <- aoc_z %>% 
  dplyr::select(c(life.stage, bio.org, effect.metric, environment, exposure.route, lvl2_f, exposure.duration.d, treatments, lvl1_f, organism.group, dose.particles.mL.master, dose.mg.L.master, effect_f, effect_10, size.length.um.used.for.conversions, density.mg.um.3, csf)) %>% 
 #filter(treatments == 4) %>% 
  filter(organism.group == "Crustacea") %>% 
  filter(exposure.duration.d == 14) %>% 
  filter(lvl1_f == "Fitness") %>% 
  #filter(life.stage == "Early") %>% 
  filter(bio.org == "organism") %>% 
 # filter(effect.metric == "NOEC") %>% 
  #filter(environment == "Marine") %>% 
  filter(exposure.route == "water") %>% 
 filter(lvl2_f == "Development")

@@

df_pred %>% ggplot(aes(x = factor(vol.L), y = ToxicityProbability)) + 
  stat_ecdf(geom = "point", size = 2, color = "blue")+
  stat_ecdf(geom = "step", linetype = 'solid', alpha = 0.6, size = 1.5) +
  #scale_x_log10() +
  scale_y_continuous(labels = scales::percent)+
  labs(title = "Cumulative Toxicity Probability",
       subtitle = "n = 1000 particles/L; Crustacea acute Development",
       caption = "Predicted Toxicity from Random Forest")
```

@@

Data_5p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Development") %>% 
  mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("5p"))
```

@@

Data_10p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Development") %>% 
  mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("10p"))
```
### 20 particles in 1 L
```{r, include=FALSE}
#rm(list=ls())
n = 20
## Generate values for the three distributions
set.seed(123)

@@

Data_20p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Development") %>% 
  mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("20p"))
```

@@

Data_40p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Development") %>% 
  mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>%  
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("40p"))
```

@@

Data_80p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Development") %>% 
  mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("80p"))
```

@@

Data_160p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Development") %>% 
  mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("160p"))
```

@@

Data_320p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Development") %>% 
 mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("320p"))
```

@@

Data_480p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Development") %>% 
 mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("480p"))
```

@@

Data_640p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Development") %>% 
 mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>%  
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("640p"))
```

@@

Data_1000p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Development") %>% 
 mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("1000p"))
```

@@

Data_1280p <- Data %>%  
  mutate(size.category = factor(case_when(
    Size < 10 & Size >= 1 ~ "1µm < 10µm",
    Size < 100 & Size >= 10 ~ "10µm < 100µm",
    Size < 1000 & Size >= 100 ~ "100µm < 1mm",
    Size < 5000 & Size >= 1000 ~ "1mm < 5mm"))) %>% 
  mutate(mass.mg = Density * Size^3 * 1E-9) %>% 
  mutate(um3 = (Size^3)) %>% 
  mutate(treatments = 4) %>% 
  mutate(organism.group = "Crustacea") %>% 
  mutate(exposure.duration.d = 14) %>% 
  mutate(lvl1_f = "Fitness") %>% 
  mutate(life.stage= "Early") %>% 
  mutate(bio.org = "organism") %>% 
  mutate(effect.metric = "NOEC") %>% 
  mutate(environment = "Marine") %>% 
  mutate(exposure.route = "water") %>% 
  mutate(lvl2_f = "Development") %>% 
 mutate(vol.mL = 1) %>% 
  mutate(vol.L = vol.mL / 1000) %>% 
  mutate(dose.um3.mL.master = um3 / vol.mL) %>% 
  mutate(dose.particles.mL.master = 1 / vol.mL) %>% 
  mutate(dose.mg.L.master = mass.mg / vol.L) %>% 
  mutate(particles.total = factor("1280p"))
```

@@

#plot dose response relationship
prob_summ %>% 
  ggplot(aes(x = particles, y = probability)) +
  geom_point() + 
  stat_smooth(method = drm, method.args = list(fct = LL.4()), se = FALSE) + #logit-4 paramater curve
  scale_x_log10(name = "Particles/mL (1-5,000 um)") +
  scale_y_continuous(labels = scales::percent_format(),
                     name = "Probability of NOEC") +
  labs(title = "Model-Predicted Probability of Toxicity",
       subtitle = "Crustacea; 14-d exp; Development; NOEC; Early; Marine",
       caption = "Random Forest Model; Simulated particle distribution (alpha = 1.6)") +
  theme_minimal(base_size = 14) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
